---
title: "lab6"
author: "Yunshan Guo"
date: "June 15, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Population Variance

Write a function `MyVar` that calculates the population variance of a vector.  If you need a refresher of what that means, [this section of wikipedia should help](https://en.wikipedia.org/wiki/Variance#Population_variance_and_sample_variance).
```{r}
MyVar=function(x){
  n=length(x)
  var(x)*((n-1)/n)
}
```


## Finding Roots
Write a function `zeroes` that finds the roots (zeroes) of a degree two polynomial.  The function should take the coefficients of the polynomial $a^2x + bx + c$ as its arguments and returns a vector of roots.  If there are no real roots, the function should stop and produce an error message: `"This polynomial has no real roots."`
```{r}
zeroes=function(a,b,c){
  delta = b^2-4*a*c
  if (b^2-4*a*c<0){
    stop("This polynomial has no real roots")
  } else if (delta==0) {
    x = (-b+sqrt(delta))/(2*a)
    str_c(x,'is the only real root of this polynomial',sep=' ')
  } else{
    x1= (-b+sqrt(delta))/(2*a)
    x2= (-b-sqrt(delta))/(2*a)
    roots= list(x1,x2)
    str_c(roots,'are the roots of this polynomial',sep=' ') 
  }
}
```


Test your function:
```{r, eval = F}
zeroes(1, 0, 0)
zeroes(1, 0, 1)
zeroes(1, 1, 1)
```

## Temperature Conversion

Write a function `ConvertTemperature` that takes a numeric vector of temperatures in Fahrenheit and converts them into Celsius, Kelvin, Rankine, Delisle, Newton, Reamur, or Romer, depending on what the user specifies in an argument called `to`.  If they specify some other temperature scale, return the message "The [their input] temperature scale is not supported".  If you don't know the conversions, (see this table)[https://en.wikipedia.org/wiki/Conversion_of_units_of_temperature#Fahrenheit]
```{r}
ConvertTemperature = function(x,to){
  if (to =='Celsius'){
    temp= (x-32)/1.8
    return (temp)
  } else if(to=='Kelvin'){
    temp= (x-32)/1.8+273.15
    return (temp)
  }else if(to=='Rankine'){
    temp = x+459.67
    return (temp)
  }else if(to=='Delisle'){
    temp = (212-x)*5/6
    return (temp)
  }else if(to=='Newton'){
    temp= (x-32)*11/60
    return (temp)
  }else if(to=='Reamur'|to=='Romer'){
    temp= (x-32)*7/24+7.5
    return (temp)
  }else{
    str_c('The',to,'temperature scale is not supported',sep=' ')
  }
}
```


Test your function
```{r, eval = F}
ConvertTemperature(32, "Celsius") == 0
ConvertTemperature(212, "Kelvin")==373.15 
ConvertTemperature(10, "Rankine") ==501.67
```


## Rolling Dice

For this problem, you'll need the `sample` and `pmax` function.  `sample` generates a random sample of a specified size either with or without replacement.  You can specify probability weights for each element of your sample space using the `prob` argument.  By default, each element will have equal probability.
```
sample(x = vector_to_be_sampled, size, replace = FALSE, prob = NULL)
```
1. What does `pmax` do? How is it different from `max`? Hint: test both on the two vectors `c(1, 5, 3)` and `c(2, 4, 2)`.

pmax is the ‘parallel’ version of the max function, meaning that it can take vector arguments and return vectors back. Max only returns the biggest value among the whole numbers. 
```{r}
max(c(1,5,3),c(2,4,2))
pmax(c(1,5,3),c(2,4,2))
```

2. When you "roll dice with advantage", you roll a pair of dice and take the higher value as your roll.  Write a function `AdvRoll` the simulates rolling with advantage `n` times. The function should take on 2 arguments `sides` and `n` and output a length `n` vector of rolls.
```{r}
AdvRoll=function(sides=6,n){
  x1=sample(seq(1:6),n,replace=T)
  x2=sample(seq(1:6),n,replace=T)
  result= pmax(x1,x2)
  return (result)
}
```

3. Write your own summary function called `MySummary` that, given a numeric vector `x`, returns the following summary statistics: mean, median, mode, sum, and sum of squares.
```{r}
Mysummary=function(x){
  ex=mean(x)
  ave=median(x)
  mod=mode(x)
  total= sum(x)
  tot_sq=sum(x^2)
  y=list(ex,ave,mod,total,tot_sq)
  return (y)
}
```

4. Using your two functions, simulate "rolling dice with advantage" 1000 times and find the summary statistics.
```{r}
x=AdvRoll(6,1000)
Mysummary(x)
```



